\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-24 paper/ms.tex
Maximum number of saves

>>>>

\subsection{Equal weight enforcement}
This value is the parameter $\beta$ described in \citet{dnest4}, and compensates
for imprecision in the spacing of the levels, so that the desired mixture
weights $w_j \propto 1$ are achieved during the second stage of the DNS
algorithm. The value 100 is recommended.

\subsection{Maximum number of saves}
This controls the length of a \pkg{DNest4} run, in units of saved particles
in {\tt sample.txt}, which represent the mixture of constrained priors.
The number of posterior samples is always less than this. In most applications
5,000 (as in the linear regression example) provides enough posterior
samples (typically a few hundred) for sufficiently accurate posterior
summaries. However, if you want to plot smooth-looking posterior histograms,
you'll need to increase this value.

If you set the maximum number of saves to zero, \pkg{DNest4} will run until
you terminate it manually.
